Summer 2024 Report

### 2025-01-28 Relations/Report.tex
defn of SR updated, table updated, counterexamples updated.

@@

  A relation $R$ is strongly recurrent (SR) if every
  $a \in A$ is $R$-strongly recurrent.
\end{dfn}
\sacomment{Not sure on this defn. Is it right to state it requires a finite number of steps}

@@

\subsection{Summary table}
BP = boundedness property

Table listing highest "confluence" property implied
by the conjunction of row and column.

\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  & CP & CR & WCR & WNFP & WUN  \\
  \midrule
  SN  & ? & CR & CR & (Should be CR?)  & ?  \\
  WN  & ? & CR & (Not CR) & ? & ? \\
  WN* & ? & CR & ? & ? & ? \\
  BP $\land$ CP & ? & CR & ? & ? & ? \\
  BP  & ? & CR & ? & ? & ? \\
  CP  & ? & CR & ? & ? & ? \\
  \bottomrule
\end{tabular}

Table listing highest "normalization" property implied
by the conjunction of row and column.

\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  & CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  &?& SN & SN & SN & SN \\
  WN  &?& (Not SN) & (Not SN) & ? & ? \\
  WN*  &?& ? & ? & ? & ? \\
  BP $\land$ CP   &?& ? & ? & ? & ? \\
  BP  &?& ? & ? & ? & ? \\
  CP  &?& (not CP or BP) & ? & ? & ? \\
  \bottomrule
\end{tabular}

@@

Unique Normal Form Property $<$ Weak Normal Form Property $<$ Recurrence Property $<$ Confluent

@@

Weakly Recurrent $<$ Weakly Normal $<$ Strongly Recurrent $<$ Weakly Normal and Strongly Recurrent $<$ Strongly Normal

The property of being strongly recurrent implies the property of being weakly normal only when there is also the classical property 
of decidability of minimality for a given element.

@@

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, CE-6  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, CE-6   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, CE-6   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - WCR }
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, \blue{CE-6}  & \blue{CE-11} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-9  & \blue{CE-3}, \blue{CE-6}  & \blue{CE-3}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
  \hline
  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
  \hline
  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \blue{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
  \hline
  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
  \hline
  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

@@

  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
  \item (Local) WCR, WR and UN $\implies$ NP 
  \item (Local) WCR, WN and UN $\implies$ SR

@@

@@

@@

>>>>

\begin{dfn}
  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step 
  from $a$ is also strongly recurrent.

  A relation $R$ is strongly recurrent (SR) if every
  $a \in A$ is $R$-strongly recurrent.
\end{dfn}

@@

  A relation $R$ is strongly recurrent (SR) if every
  $a \in A$ is $R$-strongly recurrent.
\end{dfn}
\sacomment{We have the two contender definitions for SR above.}

@@

@@

\begin{center}

  \begin{tikzpicture}[auto,
    arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
    % A box style
    \tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]

    % Place the nodes vertically (top to bottom)
    \node (Confluent) [boxnode] at (0,0) {Confluent};
    \node (RP)        [boxnode, below=2cm of Confluent] {Recurrence Property};
    \node (WN)        [boxnode, below=2cm of RP] {Weak Normal Form Property};
    \node (UN)        [boxnode, below=2cm of WN] {Unique Normal Form Property};

    % Draw arrows downwards
    \draw[arrowstyle] (Confluent) -- (RP);
    \draw[arrowstyle] (RP) -- (WN);
    \draw[arrowstyle] (WN) -- (UN);
  \end{tikzpicture}
\end{center}

@@

\begin{tikzpicture}[node distance=2cm, auto,
  % Define a thicker arrow with larger arrowhead and some shortening
  arrowstyle/.style = {->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}
]
% Define a box style
\tikzstyle{boxnode} = [draw, rectangle, minimum width=3cm, minimum height=1cm, text centered]

% Define the nodes
\node (SN) [boxnode] at (0,0) {Strongly Normal};
\node (WN) [boxnode, below left=2cm and 2cm of SN] {Weakly Normal};
\node (SR) [boxnode, below right=2cm and 2cm of SN] {Strongly Recurrent};
\node (WR) [boxnode, below of=SN, yshift=-4cm] {Weakly Recurrent};

% Draw the arrows to form a diamond
\draw [arrowstyle] (SN) -- (WN);
\draw [arrowstyle] (SN) -- (SR);
\draw [arrowstyle] (WN) -- (WR);
\draw [arrowstyle] (SR) -- (WR);
\end{tikzpicture}

The property of being strongly recurrent implies the property of being weakly recurrent only when there is also the classical property 
of decidability of minimality for a given element.

@@

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-12  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - WCR }
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10.1, CE-9  & CR, {CE-6}  & {CE-11} , {CE-9} & CR, ?  & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3.1, CE-12  & {CE-3.1}, {CE-6}  & {CE-3.1}, {CE-9}  & {CE-3.1}, {CE-3.1}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & {CE-3}, {CE-12}  & CR, {CE-6}  & CE-3, {CE-9}  & CR, {CE-3}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{WNFP} & ?, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{UN} & ?, {CE-9}  & CR, {CE-6}  & \red{CR}, {CE-9}  & CR, ?  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

@@

  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
  \item (Local) WR and UN $\implies$ NP 
  \item (Local) WN and UN $\implies$ SR

\subsection*{Counterexample 3.1}
\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {a};
      \node (a') [above of=x] {a'};
      \node (n) [left of=x, xshift=-1cm] {n \in NF};
      \node (y) [right of=x, xshift=1cm] {b};
      \node (z) [right of=y] {c};

      % Arrows
      \draw[->>] (x) -- (n);
      \draw[->] (a') -- (x);
      \draw[->] (a') -- (n);
      \draw[->>] (x) -- (y);
      \draw[->] (y) to [bend left] (z);
      \draw[->] (z) to [bend left] (y);
  \end{tikzcd}
\end{center}

Counterexample to:
\begin{itemize}
  \item (Local) WCR, WR, and UN $\implies$ NP 
  \item (Local) WCR, WN and UN $\implies$ SR

@@

          \draw[->] (f0) -- (a);
          \draw[->] (f1) -- (a);
          \draw[->] (dots) -- (a);
      \end{tikzpicture}

@@

Counterexample to:
\begin{itemize}
  \item (Local) WR, and NP $\implies$ RP 
\end{itemize}

\subsection*{Counterexample 10.1}
\begin{center}
  \begin{tikzpicture}
      % Nodes
      \node (a) {a};
      \node (a') [above of=a] {a'};
      \node (b) [left of=a, xshift=-1cm, yshift=-1cm] {b};
      \node (c) [left of=b] {c};
      \node (f0) [right of=a, xshift=1cm, yshift=-1cm] {$f_0$};
      \node (f1) [right of=f0, xshift=1cm] {$f_1$};
      \node (f2) [right of=f1, xshift=1cm] {$f_2$};
      \node (dots) [right of=f2, xshift=1cm] {...};

      % Arrows
      \draw[->] (a) -- (b);
      \draw[->] (a') -- (a);
      \draw[->] (a') -- (b);
      \draw[->] (b) to [bend left] (c);
      \draw[->] (c) to [bend left] (b);
      \draw[->] (a) -- (f0);
      \draw[->] (f0) -- (f1);
      \draw[->] (f1) -- (f2);
      \draw[->] (f2) -- (dots);
  \end{tikzpicture}
\end{center}

@@

\subsection*{Counterexample 12}
\begin{center}

  \begin{tikzcd}[node distance=2cm, auto]
      % Nodes
      \node (a) {a};
      \node (b) [right of=a, xshift=1cm] {b};
      \node (n) [below of=a, xshift=1cm] {n};

      % Arrows
      \draw[->] (a) to [bend left] (b);
      \draw[->] (b) to [bend left] (a);
      \draw[->] (a) -- (n);
  \end{tikzcd}

\end{center}
Counterexample to:
\begin{itemize}
    \item (gloabl) WCR, WR, and UN $implies$ WN or SR or SN
\end{itemize}
